---
title: "Harry Potter Data"
output: 
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(tidyverse)
library(tidytext)
```



## About

This repository contains various data files that can be used to perform a
text analysis of [Harry Potter](https://en.wikipedia.org/wiki/Harry_Potter)
books, written by Joanne Kathleen Rowling:

1) Harry Potter and the Philosopher's Stone

2) Harry Potter and the Chamber of Secrets

3) Harry Potter and the Prisoner of Azkaban

4) Harry Potter and the Goblet of Fire

5) Harry Potter and the Order of the Phoenix

6) Harry Potter and the Half-Blood Prince

7) Harry Potter and the Deathly Hallows


To perform the text analysis, we recommend using _tidyverse_ tools (see
packages below) and getting inspiration from the book 
[Text Mining with R: A Tidy Approach](https://www.tidytextmining.com/index.html)
(by Silge & Robinson):

```r
library(tidyverse)
library(tidytext)
```


-----


## Content

The content of this repo is divided in three directories, each one containing
different types of files.

- [csv-data-file/](csv-data-file) contains the text of all Harry Potter books
in a single CSV file.

- [rda-data-files/](rda-data-files) contains the seven Harry Potter books 
stored in R-Data (binary) files---one filer per book.

- [sentiment-lexicons/](sentiment-lexicons) contains a handful of sentiment 
lexicons, also stored in R-Data (binary) files---one file per lexicon.


-----


## Harry Potter CSV file

The data of all the books is available in `csv` format: 
`harry_potter_books.csv`.

Assuming that this file is in your working directory, you can import it---via
tidyverse's `readr()`---as follows:

```r
# requires package tidyverse
hp_books = read_csv("harry_potter_books.csv", col_types = "ccc")
```

```{r echo = FALSE}
hp_books = read_csv("csv-data-file/harry_potter_books.csv", col_types = "ccc")
```

This data set is fairly simple---in terms of its structure---although the 
text content is far from being tidy. The dataset has `r nrow(hp_books)` rows 
and `r ncol(hp_books)` columns: 

1) `text`: text content

2) `book`: title of associated book

3) `chapter`: associated chapter number


-----


## Harry Potter R-Data Files

The data of each book is also available in its own R-Data `rda` file
(see [rda-data-files/](rda-data-files)):

- `"philosophers_stone.rda"`
- `"chamber_of_secrets.rda"`
- `"prisoner_of_azkaban.rda"`
- `"goblet_of_fire.rda"`
- `"order_of_the_phoenix.rda"`
- `"half_blood_prince.rda"`
- `"deathly_hallows.rda"`

These files come from the R package `"harrypotter"` by Bradley Boehmke

[https://github.com/bradleyboehmke/harrypotter](https://github.com/bradleyboehmke/harrypotter)

To import these files use the `load()` function. For example, consider the
first book "Harry Potter and the Philosopher's Stone"; here's how to `load()` 
it in R:

```r
# assuming that the rda file is in your working directory
load("philosophers_stone.rda")
```

```{r echo = FALSE}
load("rda-data-files/philosophers_stone.rda")
```

Assuming that `"philosophers_stone.rda"` has been loaded, the text of this 
book is available in the homonym character vector `philosophers_stone`

```{r}
# text is in a character vector
# (with as many elements as chapters in the book)
length(philosophers_stone)
```

The number of elements in `philosophers_stone` corresponds
to the number of chapters in this book: 17 chapters.

You may want to use these files to perform bigram analysis (or other type of
n-gram analysis).


-----


## Sentiment Lexicons

In addition to the Harry Potter text, you can also find data for a handful of 
sentiment lexicons from the R package `"textdata"` (by Hvitfeldt and Silge):

- `"bing"`: Bing Liu's General purpose English sentiment lexicon that 
categorizes words in a binary fashion, either positive or negative

- `"afinn"`: AFINN is a lexicon of English words rated for valence with an
integer between minus five (negative) and plus five (positive). The words have 
been manually labeled by Finn Årup Nielsen in 2009-2011.

- `"nrc"`: General purpose English sentiment/emotion lexicon. This lexicon 
labels words with six possible sentiments or emotions: "negative", "positive",
"anger", "anticipation", "disgust", "fear", "joy", "sadness", "surprise", or
"trust". The annotations were manually done through Amazon's Mechanical Turk.

- `"loughran"`: English sentiment lexicon created for use with financial
documents. This lexicon labels words with six possible sentiments important in
financial contexts: "negative", "positive", "litigious", "uncertainty",
"constraining", or "superfluous".


These lexicons come in `rda` data files (see
[sentiment-lexicons/](sentiment-lexicons)):

- `bing.rda`
- `afinn.rda`
- `bing.rda`
- `loughran.rda`

To import them in R, use the `load()` function. For example, here's how to
import the Bing lexicon:

```r
# assuming that the rda files are in your working directory
load("bing.rda")
```

```{r echo = FALSE}
# assuming that the rda file is in your working directory
load("sentiment-lexicons/bing.rda")
```

Assuming that you've loaded the file `"bing.rda"`, the associated lexicon is 
available in the homonym tibble `bing`

```{r}
bing
```

